---
title: "Introduction to MoffittFunctions"
author: "William (Jimmy) Fulp"
date: "`r Sys.Date()`"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{Introduction to MoffittFunctions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

options(xtable.comment = FALSE, datatable.verbose = FALSE, scipen = 10, knitr.kable.NA = '', knitr.table.format = 'latex')   

```

# Overview

MoffittFunctions is a collection of useful functions designed to assist in analysis and creation of professional reports. The current MoffittFunctions functions can be broken down to the following sections:

- Testing Functions
  - two_samp_bin_test
  - two_samp_cont_test
  - cor_test
- Fancy Output Functions
  - pretty_pvalues
  - stat_paste
  - paste_tbl_group
  - pretty_model_output
  - run_pretty_model_output
  - pretty_km_output
  - run_pretty_km_output
- Utility Functions
  - round_away_0
  - get_session_info
  - get_full_name
- Example Data
  - Bladder_Cancer

### Getting Started

```{r, echo=TRUE}
# Loading MoffittFunctions and Example Dataset
library(MoffittFunctions)
data("Bladder_Cancer")
```


# Testing Functions

There are currently three testing functions, performing the appropriate statistical test depending on the data and options, and producing a p value.


## Comparing Two Groups (Binary Variable) for a Binary Variable 
 `two_samp_bin_test()` is used for comparing a binary variable to a binary (two group) variable, with parametric (t.test) and non-parametric (Wilcox Rank-Sum) options. Also pair data is allowed, where there are parametric (paired t.test) and non-parametric (Wilcox Signed-Rank) options. 

`two_samp_bin_test()`
 
 
## Comparing Two Groups (Binary Variable) for a Continuous Variable 

`two_samp_cont_test()` is used for comparing a continuous variable to a binary (two group) variable, with parametric (t.test) and non-parametric (Wilcox Rank-Sum) options. Also pair data is allowed, where there are parametric (paired t.test) and non-parametric (Wilcox Signed-Rank) options. 


## Comparing Two Continuous Variables
`cor_test()`

# Fancy Output Functions


# Utility Functions


```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
